Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-31 paper/paper.tex
impact of negative examples

\begin{figure}[t!]
  \centering
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=20 0 130 0,clip]{R/idqaccess/idqaccess.pdf}
    \caption{idqaccess}
  \end{subfigure}%
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=15 0 130 0,clip]{R/scripttag/scripttag.pdf}
    \caption{scripttag}    
  \end{subfigure}%
%\vspace{-2.5ex}  
\caption{Impact of number of positive examples.}
\label{fig:impact-number-attacks}
%\vspace{1ex}
\end{figure}

>>>>

\begin{figure}[t!]
  \centering
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=10 0 130 0,clip]{R/idqaccess/idqaccess.pdf}
    \caption{idqaccess}
  \end{subfigure}%
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=15 0 130 0,clip]{R/scripttag/scripttag.pdf}
    \caption{scripttag}    
  \end{subfigure}%
\vspace{2ex}  
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=10 0 130 0,clip]{R/coldfusion/coldfusion.pdf}
    \caption{coldfusion}
  \end{subfigure}%
    \hspace{-8ex}
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=15 0 130 0,clip]{R/inc/inc.pdf}
    \caption{inc}    
  \end{subfigure}%
    \hspace{-8ex}
  \begin{subfigure}{.2\textwidth}
    \centering
    \includegraphics[scale=0.35,trim=15 0 130 0,clip]{R/jsp/jsp.pdf}
    \caption{jsp}    
  \end{subfigure}%

%\vspace{-2.5ex}  
\caption{Impact of number of examples.}
\label{fig:impact-number-attacks}
%\vspace{1ex}
\end{figure}
